---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unriddle

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/unriddle)](https://CRAN.R-project.org/package=unriddle)
[![R-CMD-check](https://github.com/MichalLauer/unriddle/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MichalLauer/unriddle/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of unriddle is to ...

## Installation

You can install the development version of unriddle from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MichalLauer/unriddle")
```

## How to use

To enable this package, it only needs to be loaded at the beggining of you
quarto document.

````yml
---
title: My super-duper presentation
author: Michal Lauer
format: revealjs
---
```{r include=F, message=F, warning=F}`r ''`
library(unriddle)
```
````

After that, unriddling can be enabled! For example, consider the following code:

````r
```{r mtcars-plot, unriddle=TRUE}`r ''`
mtcars |> #break 
  ggplot(aes(x = factor(cyl), y = disp)) +
  geom_col() + #break
  theme_bw()
```
````
This will create three different slides. On the first one, only `mtcars` will
be showed. The second slide adds the `geom_col` layer, and finally, the third one
shows the chart with additional `theme_bw`.

## Assumptions

To unriddle a code chunk, two assumptions must be met.

1) The chunk has a unique name.
2) The `unriddle` parameter is set to `true`, e.g. `unriddle=TRUE`.

You can then add custom `#break` comments to split your chunk into multiple
slides. A brief showcase can be seen <span style="color: red">here</red>.

# Acknowledgements

First, I want to thanks to my precious girlfriend [Tereza](https://github.com/tertomas) 
who allows me to stay up all night doing nerdy stuff.

Secondly, this package is primarily inspired by the [flipbookr](https://github.com/EvaMaeRey/flipbookr) package that does basically
the same thing. When building this package, I tried to leverage more the
strengths of the knitr package as well as some javascript. Hopefully, this will
make contributing easier as the complexity of this package is (in my opinion)
much smaller. However, props to Eva for making the original stuff!
