---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unriddle

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/unriddle)](https://CRAN.R-project.org/package=unriddle)
[![R-CMD-check](https://github.com/MichalLauer/unriddle/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MichalLauer/unriddle/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of unriddle is to ...

## Installation

You can install the development version of unriddle from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MichalLauer/unriddle")
```

## How to use

To enable this package, it only needs to be loaded at the beggining of you
quarto document.

```
---
title: My super-duper presentation
author: Michal Lauer
format: revealjs
\`\`\`{r }
library(unriddle)
\`\`\`
```

To unriddle a code chunk, two assumptions must be met.

1) The chunk has a unique name.
2) The `unriddle` parameter is set to `true`, e.g. `unriddle=TRUE`.

You can then add custom `#break` comments to split your chunk into multiple
slides. A brief showcase can be seen <span style="color: red">here</red>.

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
